Rubin Observatory Scheduling Algorithm and Simulations

### 2022-10-21 ms.tex
stuff

@@

% Might be enough to discuss here to break into more figures
\begin{figure}
    \epsscale{0.5}
    \plotone{plots/cond_airmass.pdf}\plotone{plots/cond_seeing.pdf} \\
    \plotone{plots/cond_selong.pdf}\plotone{plots/cond_skybright.pdf} \\
    \plotone{plots/cond_slewtime.pdf}
    \epsscale{1}
    \caption{Information generated by the model observatory and passed to the scheduling algorithm. This is for October 1, 2023. The sun is setting with an altitude of -17 degrees. All the maps are stored as nside=32 HEALpix arrays. }
    \label{fig:conditions}
\end{figure}

>>>>

\begin{figure}
    \centering
    \epsscale{0.7}
    \plotone{plots/hours_pernight.pdf}
    \epsscale{1}
    \caption{The total amount of possible time per night and the average amount of time
after removing weather downtime. Shaded regions show scheduled downtime. Our modeled
unscheduled downtime is not included in the plot. The year progresses from left to right in
the plot starting on October 1st. The variable length June shutdown starts around Night
250. This general weather and maintenance schedule is the same for all simulations.}
    \label{fig:downtime}
\end{figure}

@@

% Might be enough to discuss here to break into more figures
\begin{figure}
    \epsscale{0.5}
    \plotone{plots/cond_airmass.pdf}\plotone{plots/cond_seeing.pdf} \\
    \plotone{plots/cond_selong.pdf}\plotone{plots/cond_skybright.pdf} \\
    \plotone{plots/cond_slewtime.pdf}
    \epsscale{1}
    \caption{Information generated by the model observatory and passed to the scheduling algorithm. These are Mollweide projections of RA,dec coordinates for October 1, 2023. Areas in gray are unreachable by the telescope because they are low altitude or in the zenith exclusion zone. The sun is setting with an altitude of -17 degrees. All the maps are stored as nside=32 HEALpix arrays. }
    \label{fig:conditions}
\end{figure}
